Structured Nonlinear Feedback Design with Separable Control-Contraction Metrics

### 2016-10-13 R0V0.tex
Changed the proof of Proposition 1. Especially, the definition of the sets E_k to be more precise with [Pak+15].

	Let the sets $\mathscr{C}_1,\ldots,\mathscr{C}_p$ be the cliques of the $\mathscr{G}$, and $\mathbin{\mathtt{card}}(\mathscr{C}_k)$ be cardinality (number of elements) of the set $\mathscr{C}_k$, $k\in\mathbb{N}_{[1,p]}$. For each index $k\in\mathbb{N}_{[1,p]}$, let the integer $\dim_k$ denote the dimension of the set $\mathbf{X}(\mathbin{\mathtt{card}}(\mathscr{C}_k))$ and define the matrix $E_k\in\mathbb{R}^{\dim_k\times n}$ as
	\begin{equation*}
		\mathbin{\mathtt{row}}(E_k,m)=\mathbin{\mathtt{row}}(I_n,m),\forall m\in\mathbb{N}_{[1,\dim_k]}\;,
	\end{equation*}	
	where $\mathbin{\mathtt{row}}(E_k,m)$ stands for the $m$-th row of the matrix $E_k$, and $I_n$ is the identity matrix with dimension $n$.

>>>>

	Let the sets $\mathscr{C}_1,\ldots,\mathscr{C}_p$ be the cliques of the $\mathscr{G}$, and $\mathbin{\mathtt{card}}(\mathscr{C}_k)$ be cardinality (number of elements) of the set $\mathscr{C}_k$, $k\in\mathbb{N}_{[1,p]}$. For each index $k\in\mathbb{N}_{[1,p]}$, let the integer $\dim_k$ denote the dimension of the set $\mathbf{X}(\mathscr{C}_k)$ and define the matrix $E_k\in\mathbb{R}^{\dim_k\times n}$ obtained from the $n\times n$ identity matrix with blocks of rows indexed by $\mathbb{N}_{[1,N]}\setminus \mathscr{C}_k$ removed.
